A Unified Treatment of Tractability for Approximation Problems Defined on Hilbert Spaces

### 2023-07-20 GeneralizedTractability2023July17.tex
Updates from Overleaf

%certain important notations for key symbols
%\newcommand{\thed}{\clubsuit}
%\newcommand{\theM}{\varheartsuit}
%\newcommand{\theUB}{\spadesuit}
\newcommand{\thed}{\delta}
\newcommand{\theM}{\mathscr{E}}
\newcommand{\theUB}{\mathscr{U}}

@@

TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas. Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc.

@@

The information complexity of the problem $\SOL_d$ is given by the function 
\[
\comp:(0,\infty) \times \naturals \to \natzero, 
\]
where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity since $d$ is typically the number of variables for the functions in $\cf_d$.

@@

In this article, we investigate a \emph{generalized tractability function}, denoted by $T$:
\begin{equation} \label{eq:Tspec}
    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty).
\end{equation}
The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$. The parameter $\vp$ is an $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative. In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.

@@

\kachi{[KACHI: I will write about notations used in this paper. Is there are need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}

We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.
In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability. We consider strong tractability when the information complexity is independent of the dimension, $d$. We then turn to tractability  when the information complexity may depend on both $d$ and $\varepsilon^{-1}$. In Section \ref{sec:examples} we provide examples of tractability functions for both the algebraic and exponential cases. We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability. In the case of generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh} \peter{[I think I do not quite understand what we mean by the last sentence.]}.

@@

Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then $\vp^* \in \cp_{\textup{trct}}$.  If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$. Thus, $\vp^* \in \cp_{\textup{trct}}$.

Thus,  $\cp_{\textup{opt}}= \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.  \qed
\end{proof}

@@

\begin{example}[Algebraic polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\vp}\}\, d^q
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
\] where in this case $\vp = (p,q)$.
Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability:
\[
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \min\{1,\lambda_{i,d}^p\}  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
Furthermore, the set of optimal $(p,q)$ is a subset of
\begin{multline*}
\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
\end{multline*}
\peter{[Is the latter statement still correct?]}
This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a}. %\fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NovWoz08a}}.
\end{example}

\begin{example}[Exponential strong polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\vp}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp=p$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for exponential strong polynomial tractability:
\begin{equation}\label{eq:exp_spt}
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^{p}}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals.
\end{equation}
In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability:
\begin{equation}\label{eq:exp_pt}
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\end{equation}
\end{example}

\peter{
In the paper \cite{KriWoz19a}, the authors derived conditions equivalent to exponential strong polynomial tractability and exponential polynomial tractability, respectively. These conditions read (with notation adapted to our present paper) as follows:
\begin{itemize}
    \item We have exponential strong polynomial tractability iff there exists a $\tau>0$ and a
    a $C\in\naturals$ such that
    \begin{equation}\label{eq:KW_exp_spt}
        \sup_{d\in\naturals} \sum_{i=C}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty.
    \end{equation}
    \item We have exponential polynomial tractability iff there exist $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$ such that
    \begin{equation}\label{eq:KW_exp_pt}
        \sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty.
    \end{equation}
\end{itemize}

\fred{Fred: Where does $p$ and/or $q$ come in conditions \eqref{eq:KW_exp_spt} and \eqref{eq:KW_exp_pt}?}

@@

Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
\[
M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
\]
for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$.
Define
\[
B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
\]
Due to our assumption, we see that $\card(B_d) < e\,M\,d^{\tau_1}$ and $\card(B_d)\le \lfloor e\,M\,d^{\tau_1} \rfloor$. Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$,
\begin{align*}
d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\qquad  + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
&\le  e\, M + \zeta (\tau_2 p).
\end{align*}
Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.

Conversely, let us now assume that Condition \eqref{eq:exp_pt} holds. We will show next that this implies Condition \eqref{eq:KW_exp_pt}. Indeed, due to \eqref{eq:exp_pt}, there exists a positive constant $M$ (w.l.o.g., we can assume that $M\ge 1$), and $p\ge 0$ (again, w.l.o.g., let us assume $p>0$), $q\ge 0$, and $L_{(p,q)}>0$ such that for all $d\in\naturals$,
\[
d^{-q}
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le M,
\]
which is equivalent to
\[
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le d^q M.
\]
Similarly to the proof of Theorem \ref{thm_main_strong_tract2}, we see that for any $n > \lceil L_{(p,q)} d^{q}\rceil $,
\[
\frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)} \le \frac{1}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty  \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)}
\le \frac{d^q M}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }.
\]
This implies that
\[
\frac{n}{d^q M}-\frac{L_{(p,q)}}{M}\le\frac{n-\lceil L_{(p,q)} d^{q}\rceil +1 }{d^q M} \le [\max\{1,\log(1+\lambda_{n+1,d}^{-1})\}]^p
\le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p.
\]
Since both $L_{(p,q)}$ and $M$ in the latter chain of inequalities are independent of $d$ and $n$, there
exists a positive constant $K$ such that
\[
\frac{n}{d^q K} \le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil,
\]
which implies
\[
\frac{n^{1/p}}{d^{q/p} K^{1/p}} -1 \le \log(1+\lambda_{n+1,d}^{-1})\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil.
\]
This, in turn, implies the existence of another constant $\widetilde{K}>0$ such that
\[
\lambda_{n,d} \le \exp\left(-\frac{n^{1/p}}{\widetilde{K}^{1/p} d^{q/p}}\right)
\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil-1,
\]
which is essentially the situation described in \cite[p.~118]{KriWoz19a}. We can then choose $\tau_2\in (0,1/p)$,
and proceed as in \cite{KriWoz19a} to obtain
\[
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \lambda_{i,d}^{i^{-\tau_2}}=\mathcal{O}(d^{q/(1-\tau_2 p)}),
\]
with the implied factor in the $\mathcal{O}$-notation independent of $d$. Then, we can choose $\tau_1=q/(1-\tau_2 p)$ and $\tau_3=q$ and see that \eqref{eq:KW_exp_pt} holds.

@@

\kachi{In the following example, we provide a brief summary of these \peter{[What does ``these'' refer to?]} notions of tractability. We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case, the roles of $\varepsilon^{-1}$ and $d$ are separated. In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments. This will allow us to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$.
%To do this, we introduce two positive-value functions that are increasing in both arguments so as to take possibly different exponents of $\varepsilon^{-1}$ and $d$.
The equivalent conditions for this example are assumed to \peter{[Why ``are assumed to?'']} take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.}

@@

We say that a problem is $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better? But obviously, you know that better than me.]} with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq  C_{\vp} \,  \phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
\]
A problem is strongly $T$-separable tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp}\,\phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals,
\] where in this case $\vp = p$ is a scalar.
Furthermore, we assume the following, which corresponds to the conditions in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
\[
\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0,
\]
since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
\[
\lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p) >0.
\]
Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau_1} \le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)
     \quad \mbox{and} \quad
      [\psi(d,q)]^{\tau_2} \le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,
\end{align*} where $\hat{K}_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $\hat{K}_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.

>>>>

%certain important notations for key symbols
%\newcommand{\thed}{\clubsuit}
%\newcommand{\theM}{\varheartsuit}
%\newcommand{\theUB}{\spadesuit}
\newcommand{\thed}{\mathscr{D}}
\newcommand{\theM}{\mathscr{E}}
\newcommand{\theUB}{\mathscr{U}}

@@

TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas. Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc. \fred{Thanks, Kachi}

@@

The information complexity of the problem $\SOL_d$ is given by the function 
\[
\comp:(0,\infty) \times \naturals \to \natzero, 
\]
where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
By definition, the \kachi{information }complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity since $d$ is typically the number of variables for the functions in $\cf_d$.

@@

In this article, we investigate a \emph{generalized tractability function}, denoted by $T$:
\begin{equation} \label{eq:Tspec}
    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty).
\end{equation}
The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$. The parameter $\vp$ is an $s$-dimensional vector with $s \geq 1$, where $\vp \geq \vzero$ implies that each component of $\vp$ is non-negative. In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.

@@

\kachi{[KACHI: I will write about notations used in this paper. Is there a need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}

We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$. The remainder of this paper is organized as follows. In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability. We consider strong tractability when the information complexity is independent of the dimension, $d$. We then turn to tractability  when the information complexity may depend on both $d$ and $\varepsilon^{-1}$. In Section \ref{sec:examples} we provide examples of tractability functions for both the algebraic and exponential cases. We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability. In the case of generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh} \peter{[I think I do not quite understand what we mean by the last sentence.]}.

@@

Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then $\vp^* \in \cp_{\textup{trct}}$.  If \kachi{$\vp^* \in \widetilde{\cp}_{\textup{trct}}$}, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.  By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$. Thus, $\vp^* \in \cp_{\textup{trct}}$.

\bigskip
\noindent This concludes the proof of Theorem \ref{thm_main_tract2}.  \qed
\end{proof}

@@

\begin{example}[Algebraic polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
\] where in this case $\vp = (p,q)$.
Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability:
\[
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \min\{1,\lambda_{i,d}^p\}  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
\kachi{[KACHI: I have questions regarding $\vp$.]}
Furthermore, the set of optimal $(p,q)$ is a subset of
\begin{multline*}
\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
\end{multline*}
\peter{[Is the latter statement still correct?] \kachi{[I think not.]}}
This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a}. %\fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NovWoz08a}}.
\end{example}

\begin{example}[Exponential strong polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\vp}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp=p$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for exponential strong polynomial tractability:
\begin{equation}\label{eq:exp_spt}
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}< \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals.
\end{equation}
In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability:
\begin{equation}\label{eq:exp_pt}
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\end{equation}
\end{example}

\peter{
In the paper \cite{KriWoz19a}, the authors derived conditions equivalent to exponential strong polynomial tractability and exponential polynomial tractability, respectively. These conditions read (with notation adapted to our present paper) as follows:
\begin{itemize}
    \item We have exponential strong polynomial tractability iff there exists a $\tau>0$ and
    a $C\in\naturals$ such that
    \begin{equation}\label{eq:KW_exp_spt}
        \sup_{d\in\naturals} \sum_{i=C}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty.
    \end{equation}
    \item We have exponential polynomial tractability iff there exist $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$ such that
    \begin{equation}\label{eq:KW_exp_pt}
        \sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty.
    \end{equation}
\end{itemize}

\fred{Fred: Where does $p$ and/or $q$ come in conditions \eqref{eq:KW_exp_spt} and \eqref{eq:KW_exp_pt}?} \kachi{[Kachi: I believe for \eqref{eq:KW_exp_spt} $p$ corresponds to $\tau$ and for \eqref{eq:KW_exp_pt} $p$ corresponds to $\tau_2$ and $q$ corresponds to both $\tau_1$ and $\tau_3$.]}

@@

Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
\[
M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
\]
for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$. Here, $M$ and other constants above may depend on $\tau_1$, $\tau_2$, and $\tau_3$.
Define $B_d$ as the set of indices that are contained in the above sum and for which the terms in the sum are relatively large:
\[
B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
\]
Due to our assumption, we see that $\card(B_d) < e\,M\,d^{\tau_1}$ and $\card(B_d)\le \lfloor e\,M\,d^{\tau_1} \rfloor$. 
Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that the term in the above sum is relatively small:
\begin{equation}
    \lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.
\label{eq:logandi}
\end{equation}

Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$, the desired sum in \eqref{eq:exp_pt} can be bounded by splitting it into the sum of the larger terms and the sum of the smaller terms:
\begin{align*}
\MoveEqLeft{d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}} \\
&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}} \qquad \text{by \eqref{eq:logandi}}\\
&\le  e\, M + \zeta (\tau_2 p).
\end{align*}
Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.

Conversely, let us now assume that Condition \eqref{eq:exp_pt} holds for some $p> 0$ and $q\ge 0$ that are assumed to be fixed. All constants in this part of the proof may depend on $p$ and $q$.  We will show next that this implies Condition \eqref{eq:KW_exp_pt}. Indeed, due to \eqref{eq:exp_pt}, there exist constants $M > 1$ and $L_{(p,q)}>0$ such that for all $d\in\naturals$,
\[
d^{-q}
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le M,
\]
which is equivalent to
\[
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le d^q M.
\]
Similarly to the proof of the sufficient condition in Theorem \ref{thm_main_strong_tract2}, we see that for any $n > \lceil L_{(p,q)} d^{q}\rceil $,
\[
\frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)} \le \frac{1}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty  \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)}
\le \frac{d^q M}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }.
\]
This inequality implies for our specific choice of $T$ that
\[
\frac{n}{d^q M}-\frac{L_{(p,q)}}{M}\le\frac{n-\lceil L_{(p,q)} d^{q}\rceil +1 }{d^q M} \le [\max\{1,\log(1+\lambda_{n+1,d}^{-1})\}]^p
\le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p.
\]
Since both $L_{(p,q)}$ and $M$ in the latter chain of inequalities are independent of $d$ and $n$, there
exists a positive constant $K$ such that
\[
\frac{n}{d^q K} \le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil,
\]
which implies
\[
\frac{n^{1/p}}{d^{q/p} K^{1/p}} -1 \le \log(1+\lambda_{n+1,d}^{-1})\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil.
\]
This, in turn, implies the existence of another constant $\widetilde{K}>0$ such that
\[
\lambda_{n,d} \le \exp\left(-\frac{n^{1/p}}{\widetilde{K}^{1/p} d^{q/p}}\right)
\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil-1,
\]
which is essentially the situation described in \cite[p.~118]{KriWoz19a}. We can then choose $\tau_2\in (0,1/p)$,
and proceed as in \cite{KriWoz19a} to obtain
\[
\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \lambda_{i,d}^{i^{-\tau_2}}=\mathcal{O}(d^{q/(1-\tau_2 p)}),
\]
with the implied factor in the $\mathcal{O}$-notation independent of $d$. Then, we can choose $\tau_1=q/(1-\tau_2 p)$ and $\tau_3=q$ and see that \eqref{eq:KW_exp_pt} holds.

@@

\kachi{In the following example, we provide a brief summary of the above examples \peter{[What does ``these'' refer to?]} of tractability. We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case, the roles of $\varepsilon^{-1}$ and $d$ are separated. In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments which will allow to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$.
%To do this, we introduce two positive-value functions that are increasing in both arguments so as to take possibly different exponents of $\varepsilon^{-1}$ and $d$.
The equivalent conditions for this example are assumed to \peter{[Why ``are assumed to?'']} take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.}

@@

We say that a problem is $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better? But obviously, you know that better than me.]} with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq  C_{\vp} \,  \phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
\]
A problem is strongly $T$-separable tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp}\,\phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals,
\] where in this case $\vp = p$ is a scalar.
Furthermore, we assume the following, which corresponds to the conditions in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
\[
\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0,
\]
since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
\[
\lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p) >0.
\]
Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau_1} \le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)
     \quad \mbox{and} \quad
      [\psi(d,q)]^{\tau_2} \le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon >0,\, d\in \naturals,
\end{align*} where $\hat{K}_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $\hat{K}_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
